---
title: "Scientific Software Licensing"
author: "Enrico"
date: "04/01/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Libraries
```{r libraries}
library(rplos)
library(rcrossref)
library(dplyr)
library(stringr)
#library(Matrix)
library(lme4)
library(ggplot2)
library(treemap)
```



#----- Get Data



## Search and download publication data 
```{r publication data}
bsd <- searchplos(q = 'bsd', 
                  fl = c("id",
                         "publication_date", 
                         "journal", 
                         "subject", 
                         "counter_total_all",
                         "alm_twitterCount", 
                         "alm_facebookCount"), 
                  limit = 100000)
bsd <- bsd$data
license <- rep("BSD", length = nrow(bsd))
bsd <- cbind(bsd, license)

mit <- searchplos(q = 'mit', 
                  fl = c("id",
                         "publication_date", 
                         "journal", 
                         "subject", 
                         "counter_total_all",
                         "alm_twitterCount", 
                         "alm_facebookCount"), 
                  limit = 100000)
mit <- mit$data
license <- rep("MIT", length = nrow(mit))
mit <- cbind(mit, license)

ecl <- searchplos(q = 'ecl', 
                  fl = c("id",
                         "publication_date", 
                         "journal", 
                         "subject", 
                         "counter_total_all",
                         "alm_twitterCount", 
                         "alm_facebookCount"), 
                  limit = 100000)
ecl <- ecl$data
license <- rep("ECL", length = nrow(ecl))
ecl <- cbind(ecl, license)

# maybe ignore
apache <- searchplos(q = 'apache', 
                     fl = c("id",
                            "publication_date", 
                            "journal", 
                            "subject", 
                            "counter_total_all",
                            "alm_twitterCount", 
                            "alm_facebookCount"), 
                     limit = 100000)
apache <- apache$data
license <- rep("Apache", length = nrow(apache))
apache <- cbind(apache, license)

mpl <- searchplos(q = 'mpl', 
                  fl = c("id",
                         "publication_date", 
                         "journal", 
                         "subject", 
                         "counter_total_all",
                         "alm_twitterCount", 
                         "alm_facebookCount"), 
                  limit = 100000)
mpl <- mpl$data
license <- rep("MPL", length = nrow(mpl))
mpl <- cbind(mpl, license)

lgpl <- searchplos(q = 'lgpl', 
                   fl = c("id",
                          "publication_date", 
                          "journal", 
                          "subject", 
                          "counter_total_all",
                          "alm_twitterCount", 
                          "alm_facebookCount"), 
                   limit = 100000)
lgpl <- lgpl$data
license <- rep("LGPL", length = nrow(lgpl))
lgpl <- cbind(lgpl, license)

gpl <- searchplos(q = 'gpl', 
                  fl = c("id",
                         "publication_date", 
                         "journal", 
                         "subject", 
                         "counter_total_all",
                         "alm_twitterCount", 
                         "alm_facebookCount"), 
                  limit = 100000)
gpl <- gpl$data
license <- rep("GPL", length = nrow(gpl))
gpl <- cbind(gpl, license)

# create main df 
SSL <- rbind(apache, bsd, ecl, gpl, lgpl, mit, mpl)


```

## Set articles appearing in more than one search to "Hybrid FOSS"
```{r hybrid licenses and duplicate id}
# get index of duplicated rows
hybridIndex <- duplicated(SSL$id)
# get index of unique rows 
nonHybridIndex <- !hybridIndex
# create hybrid df with duplicated rows
hybrid <- subset(SSL, hybridIndex)
# remove duplicates in hybrid
hybrid <- subset(hybrid, !duplicated(hybrid$id))
# set license to hybrid FOSS
hybrid$license <- "Hybrid FOSS"
# remove duplicated rows from SSL = 29708, 0 duplicates
SSL <- subset(SSL, nonHybridIndex)
# bind SSL with hybrid 
SSL<- rbind(SSL, hybrid)
```


## Get nonFOSS sample (n = 30,000, similar to n FOSS)
```{r nonFOSS sample}
nonFOSS <- data.frame()
# 6 queries downloading 5,000 articles each. The 6 words searched for are among the most common in English to produce relatively random results
for (word in c("when", "from", "one", "out", "about", "than")) {
  search <- searchplos(q = word,
                       fl = c("id",
                              "publication_date", 
                              "journal", 
                              "subject", 
                              "counter_total_all",
                              "alm_twitterCount", 
                              "alm_facebookCount"), 
                       limit = 5000)  
  nonFOSS <- rbind(nonFOSS, search$data)
  print(word)
}
license <- rep("Non-FOSS", length = nrow(nonFOSS))
nonFOSS <- cbind(nonFOSS, license)

# bind SSL to nonFOSS
SSL <- rbind(SSL, nonFOSS)

# remove duplicates from bottom. In this way, eventual FOSS articles fetched by the second query are not also counted as nonFOSS)
SSL <- distinct(SSL, id, .keep_all = TRUE)
```

## Get citation count
```{r citation count}
# note: downloading time may be long
nrow_SSL <- nrow(SSL)
citation_count <- vector(mode = "numeric", length = nrow_SSL)
loop = 0
for (row in 1:nrow_SSL) {
  x <- cr_citation_count(doi = SSL[row,"id"], 
                         url = "http://www.crossref.org/openurl/", 
                         key = "enriconardelli11@gmail.com",
                         async = FALSE)
  citation_count[row] <- x[,2] # store only citation count from the second col (ignore doi in first col)
  if (row%%20 == 0) { # print progress every 20 articles
    print(c(row, " out of ", nrow_SSL))
  }
}
print("Finished")
SSL <- cbind(SSL, citation_count = as.vector(citation_count))
```

## Write df as csv
```{r write csv}
# save raw data to csv
timeNow <- format(Sys.time(), "%y%m%d")
fileName <- paste("PLOSdata", timeNow, ".csv", sep = "")
write.csv(SSL, fileName)
```




#----- Clean Data




## Load data set
```{r load SSL}
#fileVersion <- "210722" # manually chose file version
#SSL <- read.csv(file = paste("PLOSdata", fileVersion, ".csv", sep = ""))
#SSL <- subset(SSL, select = -X) # deletes extra "X" column that appears
```

## License type
```{r license type}
SSL$license_type <- NULL
for (row in 1:nrow(SSL)) {
  if (SSL$license[row] == 'Non-FOSS') SSL$license_type[row] <- "Non-FOSS"
  else SSL$license_type[row] <- "FOSS"
}
```

## Date
```{r date}
for (row in 1:nrow(SSL)) {
  SSL$publication_date[row] <- substr(SSL$publication_date[row], 1, 10) # substring first 10 chars
}

download_date <- as.Date("2021-07-22")
SSL$download_date <- rep(download_date, length = nrow(SSL))

SSL$days_since_pub <- as.numeric(as.Date(as.character(SSL$download_date), format="%Y-%m-%d") - as.Date(as.character(SSL$publication_date), format="%Y-%m-%d"))

SSL$year <- NULL
for (row in 1:nrow(SSL)) {
  SSL$year[row] <- substr(SSL$publication_date[row], 1, 4) # substring first 10 chars
}

```

## Social media
```{r social media posts}
colnames(SSL)[which(names(SSL) == "alm_twitterCount")] <- "twitter_posts"
colnames(SSL)[which(names(SSL) == "alm_facebookCount")] <- "facebook_posts"
SSL$socialmedia_posts <- SSL$twitter_posts + SSL$facebook_posts

```

## Webpage visits
```{r webpage visits}
colnames(SSL)[which(names(SSL) == "counter_total_all")] <- "webpage_visits"
```

## Journal
```{r journal}
# Standardizes journal names (originally some were called 'PLoS', others 'PLOS')
for (row in 1:nrow(SSL)) {
  if (is.na(SSL$journal[row])) SSL$journal[row] <- "Unknown"
  else if (SSL$journal[row] == "PLOS Biology" || SSL$journal[row] == "PLoS Biology") SSL$journal[row] <- "PLOS Biology"
  else if (grepl("ONE", SSL$journal[row], fixed=TRUE)) SSL$journal[row] <- "PLOS ONE"    
  else if (grepl("Medicine", SSL$journal[row], fixed=TRUE)) SSL$journal[row] <- "PLOS Medicine"
  else if (grepl("Computational", SSL$journal[row], fixed=TRUE)) SSL$journal[row] <- "PLOS Computational Biology"
  else if (grepl("Genetics", SSL$journal[row], fixed=TRUE)) SSL$journal[row] <- "PLOS Genetics"
  else if (grepl("Pathogens", SSL$journal[row], fixed=TRUE)) SSL$journal[row] <- "PLOS Pathogens"
  else if (grepl("Tropical", SSL$journal[row], fixed=TRUE)) SSL$journal[row] <- "PLOS Neglected Tropical Diseases"
  else SSL$journal[row] <- "Other"
}
```

## Impact factor
```{r impact factor}
# Add impact factor of the journal, manually sourced from wikipedia
SSL$impact_factor <- NA
for (row in 1:nrow(SSL)) {
  if (SSL$journal[row] == "PLOS Biology") SSL$impact_factor[row] <- 7.076 
  else if (SSL$journal[row] == "PLOS ONE") SSL$impact_factor[row] <- 2.740
  else if (SSL$journal[row] == "PLOS Medicine") SSL$impact_factor[row] <- 10.500
  else if (SSL$journal[row] == "PLOS Computational Biology") SSL$impact_factor[row] <- 4.428
  else if (SSL$journal[row] == "PLOS Genetics") SSL$impact_factor[row] <- 5.174
  else if (SSL$journal[row] == "PLOS Pathogens") SSL$impact_factor[row] <- 6.218
  else if (SSL$journal[row] == "PLOS Neglected Tropical Diseases") SSL$impact_factor[row] <- 3.885
  # add a mean value for unknonw journals
  else SSL$impact_factor[row] <- mean(7.076, 2.740, 10.500, 4.428, 5.174, 6.218, 3.885)
}
```

## Subject
``` {r subject}
# extract first subject from subject list
SSL$main_subject <- "empty"
for (row in 1:nrow(SSL)) {
  if (is.na(SSL$subject[row])) {
    SSL$main_subject[row] <- "Unknown"
  } else if (SSL$subject[row] == "Unknown"){
  SSL$main_subject[row] <- "Unknown"
  } else {
  str <- str_split(SSL$subject[row], "/", simplify = TRUE) # split string at / and simplify to matrix
  SSL$main_subject[row] <- gsub(",$", "", str[,2]) # extract col 2 without eventual final commas
  }
}

for (row in 1:nrow(SSL)) {
  if (is.na(SSL$subject[row]))SSL$subject[row] <- "Unknown"
}
```

## Remove unused columns
``` {r remove columns}
SSL <- subset(SSL, select = -c(facebook_posts, twitter_posts, subject, download_date)) 
```

## Reorder columns
``` {r roerder columns}
SSL <- SSL[c("id", 
             "license", 
             "license_type",
             "citation_count",
             "socialmedia_posts",
             "webpage_visits",
             "journal",
             "impact_factor",
             "days_since_pub",
             "main_subject",
             "publication_date",
             "year")]
``` 

## Remove non complete cases
``` {r}
# Check NAs by column
apply(is.na(SSL), 2, which) 
# Remove NAs
SSL <- na.omit(SSL)
```

## Write to csv
``` {r write clean csv}
# save clean data to csv
fileName <- paste("PLOScleanData", fileVersion, ".csv", sep = "")
write.csv(SSL, fileName)
``` 





#----- Analyse Data






## Load data
```{r load}
#fileVersion <- "210722" # manually choose file version
#SSL <- read.csv(file = paste("PLOScleanData", fileVersion, ".csv", sep = ""))
#SSL <- subset(SSL, select = -X) # delete extra "X" column that appears
```

## Dataframe information
```{r df info}
dim(SSL)
summary(SSL)
```

## Tables
```{r 1D tables}
table(SSL$license)
prop.table(table(subset(SSL$license, SSL$license_type=="FOSS")))

table(SSL$license_type)
prop.table(table(SSL$license_type))

# citation count
summary(SSL$citation_count)
sd(SSL$citation_count)
summary(subset(SSL$citation_count, SSL$license_type == "FOSS"))
sd(subset(SSL$citation_count, SSL$license_type == "FOSS"))
summary(subset(SSL$citation_count, SSL$license_type == "Non-FOSS"))
sd(subset(SSL$citation_count, SSL$license_type == "Non-FOSS"))
summary(subset(SSL$citation_count, SSL$license == "Apache"))
sd(subset(SSL$citation_count, SSL$license == "Apache"))
summary(subset(SSL$citation_count, SSL$license == "BSD"))
sd(subset(SSL$citation_count, SSL$license == "BSD"))
summary(subset(SSL$citation_count, SSL$license == "ECL"))
sd(subset(SSL$citation_count, SSL$license == "ECL"))
summary(subset(SSL$citation_count, SSL$license == "GPL"))
sd(subset(SSL$citation_count, SSL$license == "GPL"))
summary(subset(SSL$citation_count, SSL$license == "LGPL"))
sd(subset(SSL$citation_count, SSL$license == "LGPL"))
summary(subset(SSL$citation_count, SSL$license == "MIT"))
sd(subset(SSL$citation_count, SSL$license == "MIT"))
summary(subset(SSL$citation_count, SSL$license == "MPL"))
sd(subset(SSL$citation_count, SSL$license == "MPL"))

# soc
summary(SSL$socialmedia_posts)
sd(SSL$socialmedia_posts)
summary(subset(SSL$socialmedia_posts, SSL$license_type == "FOSS"))
sd(subset(SSL$socialmedia_posts, SSL$license_type == "FOSS"))
summary(subset(SSL$socialmedia_posts, SSL$license_type == "Non-FOSS"))
sd(subset(SSL$socialmedia_posts, SSL$license_type == "Non-FOSS"))
summary(subset(SSL$socialmedia_posts, SSL$license == "Apache"))
sd(subset(SSL$socialmedia_posts, SSL$license == "Apache"))
summary(subset(SSL$socialmedia_posts, SSL$license == "BSD"))
sd(subset(SSL$socialmedia_posts, SSL$license == "BSD"))
summary(subset(SSL$socialmedia_posts, SSL$license == "ECL"))
sd(subset(SSL$socialmedia_posts, SSL$license == "ECL"))
summary(subset(SSL$socialmedia_posts, SSL$license == "GPL"))
sd(subset(SSL$socialmedia_posts, SSL$license == "GPL"))
summary(subset(SSL$socialmedia_posts, SSL$license == "LGPL"))
sd(subset(SSL$socialmedia_posts, SSL$license == "LGPL"))
summary(subset(SSL$socialmedia_posts, SSL$license == "MIT"))
sd(subset(SSL$socialmedia_posts, SSL$license == "MIT"))
summary(subset(SSL$socialmedia_posts, SSL$license == "MPL"))
sd(subset(SSL$socialmedia_posts, SSL$license == "MPL"))

#web
summary(SSL$webpage_visits)
sd(SSL$webpage_visits)
summary(subset(SSL$webpage_visits, SSL$license_type == "FOSS"))
sd(subset(SSL$webpage_visits, SSL$license_type == "FOSS"))
summary(subset(SSL$webpage_visits, SSL$license_type == "Non-FOSS"))
sd(subset(SSL$webpage_visits, SSL$license_type == "Non-FOSS"))
summary(subset(SSL$webpage_visits, SSL$license == "Apache"))
sd(subset(SSL$webpage_visits, SSL$license == "Apache"))
summary(subset(SSL$webpage_visits, SSL$license == "BSD"))
sd(subset(SSL$webpage_visits, SSL$license == "BSD"))
summary(subset(SSL$webpage_visits, SSL$license == "ECL"))
sd(subset(SSL$webpage_visits, SSL$license == "ECL"))
summary(subset(SSL$webpage_visits, SSL$license == "GPL"))
sd(subset(SSL$webpage_visits, SSL$license == "GPL"))
summary(subset(SSL$webpage_visits, SSL$license == "LGPL"))
sd(subset(SSL$webpage_visits, SSL$license == "LGPL"))
summary(subset(SSL$webpage_visits, SSL$license == "MIT"))
sd(subset(SSL$webpage_visits, SSL$license == "MIT"))
summary(subset(SSL$webpage_visits, SSL$license == "MPL"))
sd(subset(SSL$webpage_visits, SSL$license == "MPL"))

#year
table(SSL$year)
prop.table(table(SSL$year))

#journal
table(SSL$journal)
prop.table(table(SSL$journal))
table(subset(SSL$journal, SSL$license_type=="FOSS"))
table(subset(SSL$journal, SSL$license_type=="Non-FOSS"))

#subject
table(SSL$main_subject)
prop.table(table(SSL$main_subject))
table(subset(SSL$main_subject, SSL$license_type=="FOSS"))
table(subset(SSL$main_subject, SSL$license_type=="Non-FOSS"))

```

## Chi-Squared Test
```{r XSQR}
chisq.test(table(SSL$license, SSL$journal))
# subtract expected from actual values
table(SSL$license, SSL$journal) - chisq.test(table(SSL$license, SSL$journal))$expected

chisq.test(table(SSL$license, SSL$main_subject))
# subtract expected from actual values
table(SSL$license, SSL$main_subject) - chisq.test(table(SSL$license, SSL$main_subject))$expected

chisq.test(table(SSL$license_type, SSL$journal))
# subtract expected from actual values
table(SSL$license_type, SSL$journal) - chisq.test(table(SSL$license_type, SSL$journal))$expected

chisq.test(table(SSL$license_type, SSL$main_subject))
# subtract expected from actual values
table(SSL$license_type, SSL$main_subject) - chisq.test(table(SSL$license_type, SSL$main_subject))$expected
```

## Linear Models
```{r lm typ}
#typ
LMcit_typ <- lm(citation_count ~ license_type, data = SSL) 
summary(LMcit_typ)

LMsoc_typ <- lm(socialmedia_posts ~ license_type, data = SSL) 
summary(LMsoc_typ)

LMweb_typ <- lm(webpage_visits ~ license_type, data = SSL) 
summary(LMweb_typ)

```

```{r lm lic}
#lic
rel_license <- relevel(as.factor(SSL$license), ref = 8)

LMcit_lic <- lm(citation_count ~ rel_license, data = SSL) 
summary(LMcit_lic)

LMsoc_lic <- lm(socialmedia_posts ~ rel_license, data = SSL) 
summary(LMsoc_lic)

LMweb_lic <- lm(webpage_visits ~ rel_license, data = SSL) 
summary(LMweb_lic)
```


```{r lm fitness indices }
LMcit_soc <- lm(citation_count ~  socialmedia_posts, data = SSL) 
summary(LMcit_soc)

LMcit_web <- lm(citation_count ~  webpage_visits, data = SSL) 
summary(LMcit_web)

LMsoc_web <- lm(socialmedia_posts ~ webpage_visits, data = SSL) 
summary(LMsoc_web)

LMsoc_cit <- lm(socialmedia_posts ~citation_count, data = SSL) 
summary(LMsoc_cit)

LMweb_cit <- lm(webpage_visits ~ citation_count, data = SSL) 
summary(LMweb_cit)

LMweb_soc <- lm(webpage_visits ~ socialmedia_posts, data = SSL) 
summary(LMweb_soc)
```

## GLM Models

```{r GLM cit typ full}
GLMcit_typ <- glmer.nb(citation_count ~ license_type + as.vector(scale(impact_factor)) + as.vector(scale(days_since_pub)) + (1|journal), data = SSL, family = nbinom1(link = 'log'))

summary(GLMcit_typ)
```

```{r GLM cit lic full}
GLMcit_lic <- glmer.nb(citation_count ~ rel_license + as.vector(scale(impact_factor)) + as.vector(scale(days_since_pub)) + (1|journal), data = SSL, family = nbinom1(link = 'log'))

summary(GLMcit_lic)
```

```{r GLM soc typ full}
GLMsoc_typ <- glmer.nb(socialmedia_posts ~ license_type + as.vector(scale(impact_factor)) + as.vector(scale(days_since_pub)) + (1|journal), data = SSL, family = nbinom1(link = 'log'))

summary(GLMsoc_typ)
```

```{r GLM soc lic full}
GLMsoc_lic <- glmer.nb(socialmedia_posts ~ rel_license + as.vector(scale(impact_factor)) + as.vector(scale(days_since_pub)) + (1|journal), data = SSL, family = nbinom1(link = 'log'))

summary(GLMsoc_lic)
```

```{r GLM web typ full}
GLMweb_typ <- glmer.nb(webpage_visits ~ license_type + as.vector(scale(impact_factor)) + as.vector(scale(days_since_pub)) + (1|journal), data = SSL, family = nbinom1(link = 'log'))

summary(GLMweb_typ)
```

```{r GLM soc lic full}
GLMweb_lic <- glmer.nb(webpage_visits ~ rel_license + as.vector(scale(impact_factor)) + as.vector(scale(days_since_pub)) + (1|journal), data = SSL, family = nbinom1(link = 'log'))

summary(GLMweb_lic)
```





#----- Draw Data






```{r treemap license}
treemap(as.data.frame(table(SSL$license)),
        index="Var1",
        vSize="Freq",
        type="index",
        title="Figure 6. Proportion of Licences in the Sample")
```

```{r hist year x license}
ggplot(SSL, aes(x=as.integer(year), group=license,fill=license)) + 
    geom_histogram(position='dodge', binwidth=1)+
    xlab("Year") +
    ylab("Papers") +
    labs(title = "Figure 7",
         subtitle = "Licence Usage by Year") 
```

```{r hist year x type}
ggplot(SSL, aes(x=as.integer(year), group=license_type,fill=license_type)) + 
    geom_histogram(position='dodge', binwidth=1)+
    xlab("Year") +
    ylab("Papers") +
    labs(title = "Figure 8",
         subtitle = "Licence Type Usage by Year") 
```

```{r citcount by licence type}
ggplot(SSL, aes(x = citation_count, fill = license_type)) +
    geom_histogram(position = "dodge") +
    xlim(0, 75) +
    geom_vline(xintercept = mean(subset(SSL$citation_count, SSL$license_type == "FOSS")), linetype = "dashed",
               color = "indianred1") +
    geom_vline(xintercept = mean(subset(SSL$citation_count, SSL$license_type == "Non-FOSS")), linetype = "dashed",
               color = "cyan4") +
    xlab("Citation Count") +
    ylab("Papers") +
    labs(title = "Figure 9",
         subtitle = "Citation Count by Licence Type",
         caption = "The dashed lines represent the respective average citation counts for each group of papers.")
```

```{r soc by licence type}
ggplot(SSL, aes(x = socialmedia_posts, fill = license_type)) +
    geom_histogram(position = "dodge") +
    xlim(0, 30) +
    geom_vline(xintercept = mean(subset(SSL$socialmedia_posts, SSL$license_type == "FOSS")), linetype = "dashed",
               color = "indianred1") +
    geom_vline(xintercept = mean(subset(SSL$socialmedia_posts, SSL$license_type == "Non-FOSS")), linetype = "dashed",
               color = "cyan4") +
    xlab("Social Media Posts") +
    ylab("Papers") +
    labs(title = "Figure 10",
         subtitle = "Social Media Posts by Licence Type",
         caption = "The dashed lines represent the respective average citation counts for each group of papers.")
```

```{r web by licence type}
ggplot(SSL, aes(x = webpage_visits, fill = license_type)) +
    geom_histogram(position = "dodge") +
    xlim(0, 10^4) +
    geom_vline(xintercept = mean(subset(SSL$webpage_visits, SSL$license_type == "FOSS")), 
               linetype = "dashed",
               color = "indianred1") +
    geom_vline(xintercept = mean(subset(SSL$webpage_visits, SSL$license_type == "Non-FOSS")), 
               linetype = "dashed",
               color = "cyan4") +
    xlab("Webpage Visits") +
    ylab("Papers") +
    labs(title = "Figure 11",
         subtitle = "Webpage Visits by Licence Type",
         caption = "The dashed lines represent the respective average citation counts for each group of papers.")
```

```{r heat jou lic}
DFlic_jou <- as.data.frame(prop.table(table(SSL$license, SSL$journal)))

ggplot(DFlic_jou, aes(x=Var1, y=Var2, fill=Freq)) + 
  geom_tile() +
   xlab("License") +
    ylab("Journal") +
    labs(title = "Figure 12",
         subtitle = "Frequency of License by Journal",
         caption = "Heatmap of the Frequency of Licenses by Journal")
```

```{r heat jou lic}
DFlic_sub <- as.data.frame(prop.table(table(SSL$license, SSL$main_subject)))

ggplot(DFlic_sub, aes(x=Var1, y=Var2, fill=Freq)) + 
    geom_tile() +
    xlab("License") +
    ylab("Subject") +
    labs(title = "Figure 13",
         subtitle = "Frequency of License by Subject",
         caption = "////")
```

```{r LM cit lic residuals}
ggplot(LMcit_lic, aes(x = citation_count, y = .resid, color = rel_license)) + 
    geom_point(size = 2) +
    geom_smooth(method="lm", 
                color = "black", se = FALSE, linetype = "dashed") +
    xlab("Citation Count") +
    ylab("Residual Value")  + 
    labs(title = "Figure ///",
         subtitle = "Residuals as a Function of Citation Count",
         caption = "///")
```

```{r LM cit typ residuals}
ggplot(LMcit_typ, aes(x = citation_count, y = .resid, color = license_type)) + 
    geom_point(size = 2) +
    geom_smooth(method="lm", 
                color = "black", se = FALSE, linetype = "dashed") +
    xlab("Citation Count") +
    ylab("Residual Value")  + 
    labs(title = "Figure ///",
         subtitle = "Residuals as a Function of Citation Count",
         caption = "///")
```

```{r LM soc lic residuals}
ggplot(LMsoc_lic, aes(x = socialmedia_posts, y = .resid, color = rel_license)) + 
    geom_point(size = 2) +
    geom_smooth(method="lm", 
                color = "black", se = FALSE, linetype = "dashed") +
    xlab("Social Media Posts") +
    ylab("Residual Value")  + 
    labs(title = "Figure ///",
         subtitle = "Residuals as a Function of Social Media Posts",
         caption = "///")
```

```{r LM soc typ residuals}
ggplot(LMsoc_typ, aes(x = socialmedia_posts, y = .resid, color = license_type)) + 
    geom_point(size = 2) +
    geom_smooth(method="lm", 
                color = "black", se = FALSE, linetype = "dashed") +
    xlab("Social Media Posts") +
    ylab("Residual Value")  + 
    labs(title = "Figure ///",
         subtitle = "Residuals as a Function of Social Media Posts",
         caption = "///")
```

```{r LM web lic residuals}
ggplot(LMweb_lic, aes(x = webpage_visits, y = .resid, color = rel_license)) + 
    geom_point(size = 2) +
    geom_smooth(method="lm", 
                color = "black", se = FALSE, linetype = "dashed") +
    xlab("Webpage Visits") +
    ylab("Residual Value")  + 
    labs(title = "Figure ///",
         subtitle = "Residuals as a Function of Webpage Visits",
         caption = "///")
```

```{r LM web typ residuals}
ggplot(LMweb_typ, aes(x = webpage_visits, y = .resid, color = license_type)) + 
    geom_point(size = 2) +
    geom_smooth(method="lm", 
                color = "black", se = FALSE, linetype = "dashed") +
    xlab("Webpage Visits") +
    ylab("Residual Value")  + 
    labs(title = "Figure ///",
         subtitle = "Residuals as a Function of Webpage Visits",
         caption = "///")
```

```{r lm cit soc}
ggplot(SSL, aes(x = citation_count, y = socialmedia_posts, color = license_type)) + 
    geom_point(size = 2) +
    geom_smooth(method="lm", 
                color = "black", se = FALSE, linetype = "dashed") +
    xlab("Citation Count") +
    ylab("Social Media Posts")  + 
    labs(title = "Figure ///",
         subtitle = "Citation Count as a Function of Social Media Posts",
         caption = "///")
```



```{r LM cit typ 4 residuals}
ggplot(LMcit_typ4, aes(x = citation_count, y = .resid, color = license_type)) + 
    geom_point(size = 2) +
    geom_smooth(method="lm", 
                color = "black", se = FALSE, linetype = "dashed") +
    xlab("Citation Count") +
    ylab("Residual Value")  + 
    labs(title = "Figure LM",
         subtitle = "Residuals as a Function of Citation Count",
         caption = "///")
```

```{r LM cit lic4 residuals}
ggplot(LMcit_lic4, aes(x = citation_count, y = .resid, color = license)) + 
    geom_point(size = 2) +
    geom_smooth(method="lm", 
                color = "black", se = FALSE, linetype = "dashed") +
    xlab("Citation Count") +
    ylab("Residual Value")  + 
    labs(title = "Figure ///",
         subtitle = "Residuals as a Function of Citation Count",
         caption = "///")
```

```{r LM soc typ 4 residuals}
ggplot(LMsoc_typ4, aes(x = citation_count, y = .resid, color = license_type)) + 
    geom_point(size = 2) +
    geom_smooth(method="lm", 
                color = "black", se = FALSE, linetype = "dashed") +
    xlab("Citation Count") +
    ylab("Residual Value")  + 
    labs(title = "Figure ///",
         subtitle = "Residuals as a Function of Citation Count",
         caption = "///")
```

```{r LM soc lic 4 residuals}
ggplot(LMsoc_lic4, aes(x = citation_count, y = .resid, color = license)) + 
    geom_point(size = 2) +
    geom_smooth(method="lm", 
                color = "black", se = FALSE, linetype = "dashed") +
    xlab("Citation Count") +
    ylab("Residual Value")  + 
    labs(title = "Figure ///",
         subtitle = "Residuals as a Function of Citation Count",
         caption = "///")
```

```{r LM web typ 4 residuals}
ggplot(LMweb_typ4, aes(x = citation_count, y = .resid, color = license_type)) + 
    geom_point(size = 2) +
    geom_smooth(method="lm", 
                color = "black", se = FALSE, linetype = "dashed") +
    xlab("Citation Count") +
    ylab("Residual Value")  + 
    labs(title = "Figure ///",
         subtitle = "Residuals as a Function of Citation Count",
         caption = "///")
```


```{r GLM  cit type residuals}
GLMcit_typRES <- residuals(GLMcit_typ, "pearson", scaled = TRUE)

ggplot(SSL , aes(x = citation_count, y = GLMcit_typRES, color = license_type)) + 
    geom_point(size = 2) +
    geom_smooth(method="lm", 
                color = "black", se = FALSE, linetype = "dashed") +
    xlab("Citation Count") +
    ylab("Residual Value")  + 
    labs(title = "Figure GLM",
         subtitle = "Residuals as a Function of Citation Count",
         caption = "GLM")
```








